---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggpie - A ggplot2 extension to create pie, donut and rose pie plot

<img src = "man/figures/ggpie_hex.png" align = "right" width = "200"/>

[![CRAN](https://www.r-pkg.org/badges/version/ggpie?color=orange)](https://cran.r-project.org/package=ggpie)
[![CRAN_download](http://cranlogs.r-pkg.org/badges/grand-total/ggpie?color=blue)](https://cran.r-project.org/package=ggpie)
![License](https://img.shields.io/badge/license-MIT-green)
[![CODE_SIZE](https://img.shields.io/github/languages/code-size/showteeth/ggpie.svg)](https://github.com/showteeth/ggpie)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.6580728.svg)](https://doi.org/10.5281/zenodo.6580728)


## Introduction
`ggpie` aims to create **pie (2D and 3D)**, **donut** and **rose pie** plot with the `ggplot2` plotting system which implemented the grammar of graphics. It contains five main functions:

* `ggpie`: Create 2D pie plot with single group variable.
* `ggdonut`: Create 2D donut plot with single group variable.
* `ggnestedpie`: Create 2D nested pie plot with two group variables.
* `ggpie3D`: Create 3D pie plot with single group variable.
* `ggrosepie`: Create rose pie plot with single or two group variables.

<hr />


## Installation
You can install the released version of `ggpie` from [CRAN](https://cran.r-project.org/web/packages/ggpie/index.html) with:

```{r eval=FALSE}
install.packages("ggpie")
```

Or install the package via the [Github repository](https://github.com/showteeth/ggpie):
```{r eval=FALSE}
# install.package("remotes")   #In case you have not installed it.
remotes::install_github("showteeth/ggpie")
```

In general, it is **recommended** to install from [Github repository](https://github.com/showteeth/ggpie) (update more timely).

<hr />

## Citation
```{r citation}
citation("ggpie")
```

<hr />

## Contributing
Please note that the `ggpie` project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/1/0/0/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

<br />



