---
title: "ggpie_manual"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sample data
The sample data is from `ggplot2`:
```{r sample_data}
# load sample data
library(ggplot2)
data(diamonds)
# check data
str(diamonds)
```

## ggpie
### Introduction
[ggpie](https://github.com/showteeth/ggpie) aims to create **pie (2D and 3D)**, **donut** and **rose pie** plot with the `ggplot2` plotting system which implemented the grammar of graphics. It contains five main functions:

-   `ggpie`: Create 2D pie plot with single group variable.
-   `ggdonut`: Create 2D donut plot with single group variable.
-   `ggnestedpie`: Create 2D nested pie plot with two group variables.
-   `ggpie3D`: Create 3D pie plot with single group variable.
-   `ggrosepie`: Create rose pie plot with single or two group variables.

One of the advantages of [ggpie](https://github.com/showteeth/ggpie) is the optimization of the label, it supports two main label styles (**horizontal** and **circle**) and three label positions (**in**, **out** and **mix**).

------------------

### Installation
You can install the released version of `ggpie` from [CRAN](https://cran.r-project.org/web/packages/ggpie/index.html) with:

```{r install_with_cran}
install.packages("ggpie")
```

Or install the package via the [Github repository](https://github.com/showteeth/ggpie):

```{r install_with_gtihub}
# install.package("remotes")   #In case you have not installed it.
remotes::install_github("showteeth/ggpie")
```

Load `ggpie`:
```{r load_ggpie}
library(ggpie)
```

-----------------------

## 2D pie chart
### horizontal label
Create a pie plot with label **in the pie**:
```{r pie_horizontal_label_in}
ggpie(data = diamonds, group_key = "cut", count_type = "full",
      label_info = "all", label_type = "horizon", label_split = NULL,
      label_size = 4, label_pos = "in")
```

Create a pie plot with label **out of the pie**:
```{r pie_horizontal_label_out}
ggpie(data = diamonds, group_key = "cut", count_type = "full",
      label_info = "all", label_type = "horizon",
      label_size = 4, label_pos = "out" )
```

Create a pie plot with **mixture label**:
```{r pie_horizontal_label_mixture}
ggpie(data = diamonds, group_key = "cut", count_type = "full",
      label_info = "all", label_type = "horizon", label_split = NULL,
      label_size = 4, label_pos = "in", labal_threshold = 10)
```

-----------------------

### circle label
Create a pie plot with label **in the pie**:
```{r pie_circle_label_in}
ggpie(data = diamonds, group_key = "cut", count_type = "full",
      label_info = "all", label_type = "circle", label_split = NULL,
      label_size = 4, label_pos = "in")
```

Create a pie plot with label **out of the pie**:
```{r pie_circle_label_out}
ggpie(data = diamonds, group_key = "cut", count_type = "full",
      label_info = "all", label_type = "circle",label_split = NULL,
      label_size = 4, label_pos = "out")
```

Please notice that, <mark>create a pie plot with circle label does not support mixture label</mark>.

-----------------------

### split label
Besides adding **horizontal** and **circle** labels, `ggpie` also support split the label with regex. By default, ggpie will split the label by spaces (`[[:space:]]+`):
```{r split_label}
ggpie(data = diamonds, group_key = "cut", count_type = "full",
      label_info = "all", label_type = "horizon", label_split = "[[:space:]]+",
      label_size = 4, label_pos = "out" )
```

Please notice that, <mark>spliting the label is support by all available tools in `ggpie` (`ggpie`, `ggdonut`, `ggnestedpie`, `ggpie3D`, `ggrosepie`)</mark>.

-----------------------

## 3D pie chart
3D pie chart is adopted and modified from [ggthreed](https://github.com/coolbutuseless/ggthreed):
```{r pie_3D}
p1= ggpie3D(data = diamonds, group_key = "cut", count_type = "full", tilt_degrees = -10, label_size=2) + 
  ggtitle("tilt_degrees = -10") + 
  theme(plot.title = element_text(hjust = 0.5))

p2= ggpie3D(data = diamonds, group_key = "cut", count_type = "full", tilt_degrees = -40, label_size=2) + 
  ggtitle("tilt_degrees = -40") + 
  theme(plot.title = element_text(hjust = 0.5))

p3= ggpie3D(data = diamonds, group_key = "cut", count_type = "full", tilt_degrees = -10, 
            start_degrees = 60, label_size=2) + 
  ggtitle("start_degrees = 60") + 
  theme(plot.title = element_text(hjust = 0.5))

p4= ggpie3D(data = diamonds, group_key = "cut", count_type = "full", tilt_degrees = -10, 
            start_degrees = 180, label_size=2) + 
  ggtitle("start_degrees = 180") + 
  theme(plot.title = element_text(hjust = 0.5))

cowplot::plot_grid(p1,p2,p3,p4,ncol = 2)
```

-----------------------

## Donut plot
### horizontal label
Create a donut plot with label **in the pie**:
```{r donut_horizontal_label_in}
ggdonut(data = diamonds, group_key = "cut", count_type = "full",
        label_info = "all", label_type = "horizon", label_split = NULL,
        label_size = 4, label_pos = "in")
```

Create a donut plot with label **out of the pie**:
```{r donut_horizontal_label_out}
ggdonut(data = diamonds, group_key = "cut", count_type = "full",
        label_info = "all", label_type = "horizon", label_split = NULL,
        label_size = 4, label_pos = "out")
```

Create a donut plot with **mixture label**:
```{r donut_horizontal_label_mixture}
ggdonut(data = diamonds, group_key = "cut", count_type = "full",
        label_info = "all", label_type = "horizon",
        label_size = 4, label_pos = "in", labal_threshold = 10)
```

-----------------------

### circle label
Create a donut plot with label **in the pie**:
```{r donut_circle_label_in}
ggdonut(data = diamonds, group_key = "cut", count_type = "full",
        label_info = "all", label_type = "circle", label_split = NULL,
        label_size = 4, label_pos = "in")
```

Create a donut plot with label **out of the pie**:
```{r donut_circle_label_out}
ggdonut(data = diamonds, group_key = "cut", count_type = "full",
        label_info = "all", label_type = "circle",
        label_size = 4, label_pos = "out")
```

-----------------------

## Nested pie/donut plot
It is often the case that we have **two categorical variables** and then need to plot for both of them, `ggnestedpie` is designed to deal with this.

### inner and outer are circle labels
**inner circle label** and **no split**, **outer circle label** and **in** pie plot
```{r nested_pie_inner_outer_circle_in}
ggnestedpie(data = diamonds, group_key = c("cut", "color"), count_type = "full",
            inner_label_info = "all", inner_label_split = NULL,inner_label_size = 2,
            outer_label_type = "circle", outer_label_pos = "in", outer_label_info = "all")
```

**inner circle label** and **no split**, **outer circle label** and **in** pie plot, **remove fraction below 1 of inner pie**:
```{r nested_pie_inner_outer_circle_in_remove}
ggnestedpie(data = diamonds, group_key = c("cut", "color"), count_type = "full",
            inner_label_info = "all", inner_label_split = NULL,
            inner_labal_threshold = 5, inner_label_size = 2,
            outer_label_type = "circle", outer_label_pos = "in", outer_label_info = "all")
```

**inner circle label** and **no split**, **outer circle label** and **out** of pie plot:
```{r nested_pie_inner_outer_circle_out}
ggnestedpie(data = diamonds, group_key = c("cut", "color"), count_type = "full",
            inner_label_info = "all", inner_label_split = NULL, inner_label_size = 2,
            outer_label_type = "circle", outer_label_pos = "out", outer_label_info = "all")
```

-----------------------

### inner circle label and outer horizontal label
**inner circle label** and **no split**, **outer horizontal label** and **out** of pie plot, **remove fraction below 1 of inner pie**:
```{r nested_pie_inner_outer_horizon_out_remove}
ggnestedpie(data = diamonds, group_key = c("cut", "color"), count_type = "full",
            inner_label_info = "all", inner_label_split = NULL,
            inner_labal_threshold = 1, inner_label_size = 2,
            outer_label_type = "horizon", outer_label_pos = "out", outer_label_info = "all")
```

**inner circle label** and **no split**, **outer horizontal label** and **in** pie plot, **remove fraction below 1 of inner pie**, **adjust fraction below 10 to out of pie of outer pie plot**:
```{r nested_pie_inner_outer_remove_horizon_in_remove}
ggnestedpie(data = diamonds, group_key = c("cut", "color"), count_type = "full",
            inner_label_info = "all", inner_label_split = NULL,
            inner_labal_threshold = 1, inner_label_size = 2,
            outer_label_type = "horizon", outer_label_pos = "in",
            outer_label_info = "all", outer_labal_threshold = 10)
```

-----------------------

### blank between plot
Add blank between inner and outer plot:
```{r nested_pie_blank_inner_outer}
ggnestedpie(data = diamonds, group_key = c("cut", "color"), count_type = "full", 
            r0 = 0.5, r1 = 1.5, r2 = 2.6,inner_label_info = "all", inner_label_split = NULL,
            inner_labal_threshold = 1, inner_label_size = 2,
            outer_label_type = "horizon", outer_label_pos = "in",
            outer_label_info = "all", outer_labal_threshold = 10)
```

-----------------------

## Rose pie/donut plot
### single variable
**do not show tick**:
```{r rose_pie_no_tick, fig.height=10, fig.width=18}
# pie plot
p1=ggrosepie(diamonds, group_key = "color", count_type = "full", label_info = "all",
             show_tick=F,donut_frac=NULL)
# donut plot
p2=ggrosepie(diamonds, group_key = "color", count_type = "full", label_info = "all",
             show_tick=F,donut_frac=0.3,donut_label_size=3)
cowplot::plot_grid(p1,p2)
```

**show tick** and **select breaks automaticly**:
```{r rose_pie_with_tick, fig.height=8, fig.width=18}
# pie plot
p1=ggrosepie(diamonds, group_key = "color", count_type = "full", label_info = "all",
             donut_frac=NULL)
# donut plot
p2=ggrosepie(diamonds, group_key = "color", count_type = "full", label_info = "all",
             donut_frac=0.3,donut_label_size=3)
cowplot::plot_grid(p1,p2)
```

**show tick** and **with specific breaks**:
```{r rose_pie_with_tick_specific_break, fig.height=8, fig.width=18}
# pie plot
p1=ggrosepie(diamonds, group_key = "color", count_type = "full", label_info = "all",
             tick_break = c(3000,5000,7000,11000), donut_frac=NULL)
# donut plot
p2=ggrosepie(diamonds, group_key = "color", count_type = "full", label_info = "all",
             tick_break = c(3000,5000,7000,11000), donut_frac=0.3,donut_label_size=3)
cowplot::plot_grid(p1,p2)
```

-----------------------

### two variables
**do not show tick**:
```{r rose_pie_two_no_tick, fig.height=8, fig.width=18}
# pie plot
p1=ggrosepie(diamonds, group_key = c("color","clarity"),
             count_type = "full", label_info = "all",
             show_tick=F,donut_frac=NULL)
# donut plot
p2=ggrosepie(diamonds, group_key = c("color","clarity"),
             count_type = "full", label_info = "all",
             show_tick=F,donut_frac=0.3,donut_label_size=3)
cowplot::plot_grid(p1,p2)
```

**show tick** and **select breaks automaticly**:
```{r rose_pie_two_with_tick, fig.height=8, fig.width=18}
# pie plot
p1=ggrosepie(diamonds, group_key = c("color","clarity"),
             count_type = "full", label_info = "all",
             donut_frac=NULL)
# donut plot
p2=ggrosepie(diamonds, group_key = c("color","clarity"),
             count_type = "full", label_info = "all",
             donut_frac=0.3,donut_label_size=3)
cowplot::plot_grid(p1,p2)
```

**show tick** and **with specific breaks**:
```{r rose_pie_two_with_tick_specific_break, fig.height=8, fig.width=18}
# pie plot
p1=ggrosepie(diamonds, group_key = c("color","clarity"),
             count_type = "full", label_info = "all",
             tick_break = c(3000,5000,7000,11000), donut_frac=NULL)
# donut plot
p2=ggrosepie(diamonds, group_key = c("color","clarity"),
             count_type = "full", label_info = "all",
             tick_break = c(3000,5000,7000,11000), donut_frac=0.3,donut_label_size=3)
cowplot::plot_grid(p1,p2)
```

-----------------------














